### 2025-05-26 conteudo/results/students.tex
fix small typos on text
finish work of 25-05

\section{Students}

@@

\subsection{Questionary Answers}

@@

>>>>

\section{Study with University Students}

@@

\subsection{Survey Results Analysis}

@@

\subsection{Students Contribution to the Tool}

For the two groups opted to contribute directly to the ArKanjo tool development, 
we listed multiple issues existed in the tool. The first group opted for working 
in expand the tool suport for multiple operation systems. Some libraries used in the 
tool development only had support for the Ubuntu distribution, and the first group was 
responsible to migrate these libraries to libraries that have support to multiple operation
systems. This issue was of our knowledge and pointed by the teaching assistant in the survey, as 
he faced the issue while using the tool.

The second group opted for working in a webpage for the tool documentation and support 
for light and dark mode. The colored output presented in the figures in Chapter \ref{cha:tool} 
were hard coded at first, does not considering the user terminal colors, 
thus giving a bad user experience. The website is helpfull to 
faciliate people to contribute or use the tool. We did not know how to approach the light and 
dark mode at first and have not needed to look on how
to fix the issue as the group search and found a solution on his own.

The students successfully delivered the issues fix proposed. We found interesting to see 
people able to contribute to the tool on issues that even us did not know how to approach.
The issues helps the user experience and facilitates other researches using the ArKanjo tool 
that we may explore in future works. Appendix \ref{app:contribution} has references to the
students contributions, the issue list proposed to the students and figures of the 
documentation webpage.
